\toolnameend: A Tool for Visualizing Patterns of Spreadsheet Function Combinations

### 2016-08-08 doc/paper.tex
Viz work, anonymous acks.
Unscalability comments -- fixes #145

	The participants were most vocal about their findings when they discovered, by
	purpose or accident, instances of heinous design in the dataset. Many times,
	they noted these examples shortly after opening a new tree, suggesting that the
	distinctive visual signatures as discussed in Section \ref{badsmells} was a
	salient force in their exploration. For example, when P3 encountered the
	initial design of the SUM tree, as seen in Figure \ref{fig:sum}, they readily
	diagnosed that either a spreadsheet author was "totally incompetent, or [the
	formula was] just something that's weird." Other than these visual cues, value
	errors, prefixed with \#s, also appear in the tree, which P4 said could be
	useful for tracking these problems if marked well.

@@

	Additionally, because the files in the Enron set had name with the author as a
	prefix, P2 commented that they could use the tool in a company setting to
	follow up with repeat offenders. For instance, they first encountered a
	particular author's name when investigating an AVERAGE function with 18
	distinct arguments for which our participant could not discern any logical
	order even after opening the source spreadsheet; the same name popped up again
	as P2 looked at a RATE function relying on several hard-coded values. P2 said
	that, if they were a manager or project leader, this recurrence was a sign to
	talk to the author personally and figure out why these problems were there, as
	to prevent more in the future. They also added that these problems would grow
	worse if this particular author left the company and no one remained who
	understood these formulae, a concern that aligns with Hermans' transfer
	scenarios \cite{hermans2011supporting}.

	The detection of bad design, however, is certainly not limited to a
	visualization tool, and some users remarked that a tool which printed a list of
	errors could suffice just as well for that purpose. However, they also remarked
	that this visual interface better supports the case when searching for new and
	previously unknown smells. Because the exploratory design makes no
	qualitative judgment and visualizes benign designs with the problematic, it
	therefore allows for flexible interpretation of what is a smell; that is, a
	user might not realize a certain design is suboptimal until they see it in the
	tree and, at the point, find specific examples of where it occurs in the
	spreadsheets.

@@

	% use section* for acknowledgment
	\section*{Acknowledgment} This material is based upon work supported in whole
	or in part with funding from the Laboratory for Analytic Sciences (LAS). Any
	opinions, findings, conclusions, or recommendations expressed in this material
	are those of the author(s) and do not necessarily reflect the views of the LAS
	and/or any agency or entity of the United States Government.

>>>>

	The participants were most vocal about their findings when they discovered, by
	purpose or accident, instances of heinous design in the dataset. Many times,
	they noted these examples shortly after opening a new tree, suggesting that the
	distinctive visual signatures as discussed in Section \ref{badsmells} was a
	salient force in their exploration. For example, when P3 encountered the
	initial design of the SUM tree, as seen in Figure \ref{fig:sum}, they readily
	diagnosed that either a spreadsheet author was "totally incompetent, or [the
	formula was] just something that's weird." Even though the visualization struggles
	to scale well for this formula, it calls clearly to a problem in the underlying
	spreadsheets -- awkward formulae make awkward trees. Other than these visual cues, value
	errors, prefixed with \#s, also appear in the tree, which P4 said could be
	useful for tracking these problems if marked well.

@@

	Additionally, because the Enron files had names with the author as a
	prefix, P2 commented that companies could use the tool to
	follow up with repeat offenders. For instance, they first encountered a
	particular author's name when investigating an AVERAGE function with 18
	distinct arguments for which our participant could not discern any logical
	order even after opening the source spreadsheet; the same name popped up again
	as P2 looked at a RATE function relying on several hard-coded values. P2 said
	that, if they were a manager or project leader, this recurrence was a sign to
	talk to the author personally and figure out why these problems were there, as
	to prevent more in the future. They also added that these problems would grow
	worse if this particular author left the company and no one remained who
	understood these formulae, a concern that aligns with Hermans' transfer
	scenarios \cite{hermans2011supporting}.

	The detection of bad design, however, is certainly not limited to a
	visualization tool, and some users remarked that a tool which printed a list of
	errors could work just as well for that purpose. However, they also said
	that this visual interface is better when searching for new smells. 
	Because the exploratory design makes no
	qualitative judgment and visualizes benign designs with the problematic, it
	allows for flexible interpretation of what a smell is; that is, a
	user might not realize a certain design is poor until they see it in the
	tree and, at the point, find specific examples of where it occurs in the
	spreadsheets.

@@

	% use section* for acknowledgment
	\section*{Acknowledgment} This material is based upon work supported in whole
	or in part with funding from the Laboratory for Analytic Sciences (LAS). Any
	opinions, findings, conclusions, or recommendations expressed in this material
	are those of the author(s) and do not necessarily reflect the views of the LAS
	and/or any agency or entity of the United States Government. I also thank the
	anonymous reviewers who advised the direction of this paper.
